---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DRtool

<!-- badges: start -->
<!-- badges: end -->

DRtool provides an interactive tool used to analyze clusterings of high-dimensional
data. The minimum spanning tree is used in a manifold-learning process to approximate
the high-dimensional data's distribution. Various analytical plots provide a
multi-faceted perspective on the dimension reduction results to help distinguish
signal from byproducts of the dimension reduction process.

## Installation

You can install the development version of DRtool from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("JustinMLin/DRtool")
```

## Example

To run an example on the [MNIST](https://en.wikipedia.org/wiki/MNIST_database) data:

```{r example}
library(DRtool)

# parallel computing is not available on Windows
run_example(cluster="real", parallel=FALSE)
```
