---
title: "DRtool"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DRtool}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette provides an example of the DRtool workflow from start to finish,
including preparing the data and using the tool. We will use the MNIST data set
available in [dslabs](https://cran.r-project.org/web/packages/dslabs/index.html),
as well as an implementation of UMAP available in
[umap](https://cran.r-project.org/web/packages/umap/index.html). This package
implements the UMAP algorithm in both R and Python. The Python implementation
is more efficient, but requires a Python installation setup with
[reticulate](https://cran.r-project.org/web/packages/reticulate/index.html) and
the Python package [umap-learn](https://umap-learn.readthedocs.io/en/latest/).

## Preparing the data

We start by importing the data. The imported data contains 70,000 images
partitioned into a training set and a test set containing 60,000 and 10,000
images, respectively. Each image is a 28 x 28 pixel image of a handwritten
digit. When vectorized, each image is represented by a 784-dimensional vector.
Since we are not performing cross-validation, we may disregard the test set. For
sake of computation, we randomly sample 2,000 images from the training set.

```{r import data}
library(dslabs)

import <- read_mnist()
images <- import$train$images
labels <- import$train$labels

subsample <- sample(1:length(labels), 2000)

Z <- images[subsample,]
true_labels <- labels[subsample]
```

In line with the typial UMAP workflow, we apply a PCA pre-processing step. This
step will begin the de-noising process and speed up the UMAP computation.

```{r PCA pre-processing}
Z_pca <- unname(prcomp(Z, rank. = 300)$x)
```

## Creating the low-dimensional embedding

Note, this step is highly specialized to the data being studied. We provide an
example of this process, but analysts should carefully consider how to construct
a low-dimensional embedding of their own data.

To create the low-dimensional embedding, we apply UMAP using the implementation
in [umap](https://cran.r-project.org/web/packages/umap/index.html). The Python
implementation provided by the package is recommend for its efficiency, but it
requires a Python installation setup with
[reticulate](https://cran.r-project.org/web/packages/reticulate/index.html) and
the Python package [umap-learn](https://umap-learn.readthedocs.io/en/latest/).
For ease of reproducibility, we resort to the provided R implementation.

```{r low-dimensional embedding}
library(umap)

X <- umap(Z_pca, method="naive", n_neighbors=30)$layout
```

## Running the tool

To run the tool, the required inputs are the high-dimensional data,
low-dimensional embedding, and cluster labels. We also supply the indices of the
randomly sampled images to serve as IDs. Optionally, the user may also provide
a dist object or distance matrix for the high-dimensional data. By default,
the distance matrix is calculated using Euclidean distance. This matrix is used
in the construction of the minimum spanning tree.

```{r run tool, eval=FALSE}
library(DRtool)

run_app(Z=Z, X=X, cluster=true_labels, id=subsample)
```

In practice, the true class labels might not be available. To replicated this
situation, we can run the tool using a calculated k-means clustering.

```{r run tool kmeans, eval=FALSE}
kmeans_cluster = kmeans(Z_pca, centers=10, iter.max=100, nstart=20)$cluster

run_app(Z=Z, X=X, cluster=kmeans_labels, id=subsample)
```
