---
title: "DRtool"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DRtool}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette provides an example of the DRtool workflow from start to finish,
including preparing the data and using the tool. We will use the MNIST data set
available in [dslabs](https://cran.r-project.org/package=dslabs),
as well as an implementation of UMAP available in
[umap](https://cran.r-project.org/package=umap). This package
implements the UMAP algorithm in both R and Python. The Python implementation
is more efficient, but requires a Python installation setup with
[reticulate](https://cran.r-project.org/package=reticulate) and
the Python package [umap-learn](https://umap-learn.readthedocs.io/en/latest/).

## Preparing the data

We start by importing the data. The imported data contains 70,000 images
partitioned into a training set and a test set containing 60,000 and 10,000
images, respectively. Each image is a 28 x 28 pixel image of a handwritten
digit. When vectorized, each image is represented by a 784-dimensional vector.
Since we are not performing cross-validation, we may disregard the test set. For
sake of computation, we randomly sample 2,000 images from the training set.

```{r import data}
library(dslabs)

import <- read_mnist()
images <- import$train$images
labels <- import$train$labels

subsample <- sample(1:length(labels), 2000)

Z <- images[subsample,]
true_labels <- labels[subsample]
```

In line with the typial UMAP workflow, we apply a PCA pre-processing step. This
step will begin the de-noising process and speed up the UMAP computation.

```{r PCA pre-processing}
Z_pca <- unname(prcomp(Z, rank. = 300)$x)
```

## Creating the low-dimensional embedding

Note, this step is highly specialized to the data being studied. We provide an
example of this process, but analysts should carefully consider how to construct
a low-dimensional embedding of their own data.

To create the low-dimensional embedding, we apply UMAP using the implementation
in the R package [umap](https://cran.r-project.org/package=umap).
The Python implementation provided by the package is recommend for its
efficiency, but it requires a Python installation setup with
[reticulate](https://cran.r-project.org/package=reticulate) and
the Python package [umap-learn](https://umap-learn.readthedocs.io/en/latest/).
For ease of reproducibility, we resort to the provided R implementation.

```{r low-dimensional embedding}
library(umap)

# X <- umap(Z_pca, method="umap-learn", n_neighbors=30)$layout
X <- umap(Z_pca, method="naive", n_neighbors=30)$layout
```

## Running the tool

To run the tool, the required inputs are the high-dimensional data,
low-dimensional embedding, and cluster labels. We also supply the indices of the
randomly sampled images to serve as IDs and a vector of column names (PC1, PC2,
...). Optionally, the user may also provide a dist object or distance matrix
for the high-dimensional data if the default Euclidean distance is not desired.
These distances are used to construct the minimum spanning tree. Lastly, the
user may also take advantage of parallel computing. Parallel computing is used
when simulating the null distributions for the MST test. The implementation
uses [mclapply()](https://www.rdocumentation.org/packages/parallel/versions/3.4.0/topics/mclapply)
from the [parallel](https://www.rdocumentation.org/packages/parallel/versions/3.6.2).
Unfortunately, it is not available for Windows machines.

```{r run tool, eval=FALSE}
library(DRtool)

col_names <- sapply(1:300, function(i) paste0("PC", i))
run_app(Z=Z_pca, X=X, cluster=true_labels, id=subsample, col_names=col_names, parallel=TRUE)
```

In practice, the true class labels might not be available. To replicate this
situation, we can run the tool using a calculated k-means clustering.

```{r run tool kmeans, eval=FALSE}
kmeans_cluster <- kmeans(Z_pca, centers=10, iter.max=100, nstart=20)$cluster

run_app(Z=Z, X=X, cluster=kmeans_labels, id=subsample)
```
